moderated_regressions

### 2024-05-14 moderated_regressions.Rmd
changing plots

cr_eng_plot <- interact_plot(cr_eng_m3u, pred = overall.challenge_center, modx = overall.resource_center, interval = TRUE,
              int.width = 0.8)
cr_eng_plot
```

@@

hr_stress_plot <- interact_plot(hr_stress_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = TRUE,
              int.width = 0.8)
hr_stress_plot
```

@@

hr_burn_plot <- interact_plot(hr_burn_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = TRUE,
              int.width = 0.8)
hr_burn_plot
```

>>>>

cr_eng_plot <- interact_plot(cr_eng_m3u, pred = overall.challenge_center, modx = overall.resource_center, interval = FALSE,
              int.width = 0.8)
cr_eng_plot
```

@@

hr_stress_plot <- interact_plot(hr_stress_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = FALSE, 
              int.width = 0.8)
hr_stress_plot
```

@@

hr_burn_plot <- interact_plot(hr_burn_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = FALSE, 
              int.width = 0.8)
hr_burn_plot
```
